---
title: "Week4ProjectPrestentation"
author: "kagauss"
date: "December 6, 2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
---
##Shiny Project App

This app is used to predict a cars MPG based on the HP input of the user.  It is an interactive linear model regression that updates the red "predicted value" in a reactive manner.

---

The dataset is loaded into the app and a linear regression is performed using hp as the predictor varaible and mpg as the response variable.
```{r}
data("mtcars")
fit <- lm(mpg~hp, data = mtcars)  
```

Ex. The user slides the bar in the app to hp = 100
---
```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
```

```{r, echo=FALSE, message=FALSE}
p <- ggplot(data = mtcars, aes(x = hp, y = mpg))+geom_point()+geom_smooth(method = "lm")+
    geom_point(size = 5, color = "red", aes(x=100, y=coef(fit)[1] + 100 * coef(fit)[2]))
      
ggplotly(p)
```

---

The app can be further expanded upon by adding addtional predictor variables for a more accurate prediction on a cars MPG.